### 2011-12-09 AffineLieAlgebras/Thesis/4.tex
More translations in SLE section

In paper \cite{schramm2000scaling} it was shown that $g_{t}(z)$ satisfies stochastic differential equation 
\begin{equation}
\label{eq:19}
  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
\end{equation}
where $\xi_{t}$ is the Brownian motion. The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.

Stochastic process which satisfies \eqref{eq:19} is called     {\it Schramm-Loewner evolution} on the upper half-plane $\mathbb{H}$.
For us it is more convenient to use map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
\begin{equation}
  \label{eq:20}
       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}  
\end{equation}
Schramm-Loewner evolution provides conformally-invariant probability measure on curves $\gamma_{t}$ in $\mathbb{H}$.

\subsection{SLE martingales and CFT correlation functions}
\label{sec:corr-betw-sle}

Now we can look at the observables in the presence of SLE trace. Expectation value of lattice observable $\mathcal{O}$ on the upper half-plane can be calculated as the sum of expectation values of this observable in presence of SLE trace $\gamma_{t}$ up to some time $t$ multiplied by the probability of this trajectory:
\begin{equation*}
  \prec \mathcal{O} \succ_{\mathbb{H}}=\mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=\sum_{\gamma_{t}} P\left[C_{\gamma_{t}}\right] \prec \mathcal{O} \succ_{\gamma_{t}}
\end{equation*}
Lattice observable  $\prec \mathcal{O} \succ_{\mathbb{H}}$ does not depend on $t$, hence $\prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale.

In continuous limit lattice observable tends to CFT correlation function \cite{bauer2003sle,bauer2003conformal,bauer2002sle}.
We need to take into account the change of boundary conditions on the tip of SLE trace and at the infinity, so the expression is
\begin{equation}
  \prec \mathcal{O} \succ_{\mathbb{H}_{t}}\to \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}
%% =
%%   \frac{\left<^{g_{t}}
%% \mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
\label{eq:21}
\end{equation}

%% Here $\phi(z_{t})$ is a primary field corresponding to boundary condition changing operator.
%% We've used the conformal map $g_{t}$ to get the expression on the whole plane in equation \eqref{eq:21}.

We consider the theory with the boundary, so in principle we need to use boundary conformal field theory here and impose proper consistency conditions \cite{cardy1984conformal,cardy1989boundary,cardy1991bulk}. In the case of upper half-plane correlation functions of boundary CFT can be rewritten as the correlation functions of the theory on the whole plane but with doubled number of bulk fields.

@@

We assume that $\mathcal{F}$ contains some set of primary fields $\varphi_{\lambda_{i}}$ with conformal weights $h_{\lambda_{i}}$. Since we work with boundary CFT we need to add bulk fields in conjugate points $\bar z_{i}$. For future use in WZNW models we denote the conformal weights of these duplicate fields by $h_{\lambda_{i}^{*}}$.  Also we have boundary condition changing operators  $\phi$ at the tip of SLE trace and at the infinity.  We use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite expression \eqref{eq:21} in the whole upper half plane:

\begin{equation}
  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
  \label{eq:1}
\end{equation}

Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:1}) gives us
\begin{equation*}
  -\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}.
\end{equation*}
For transformation of primary fields $\varphi_{\lambda_{i}}$ we have 
\begin{equation}
  \label{eq:2}
  d\varphi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\varphi_{\lambda_{i}}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\varphi_{\lambda_{i}}(w_{i}) 
\end{equation}
We denote generator of this transform by $\mathcal{G}_{i}$.

Since $ \prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale, the expectation value of its increment during the evolution from $t$ to $t+dt$ is zero
\begin{equation}
  \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=    \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t+dt}}\right], \quad d\mathbb{E}\left[ \prec\mathcal{O}\succ_{\gamma_{t}}\right]=0
\label{eq:22}
\end{equation}
Using Ito calculus we get the expression for the differential of $\mathcal{F}$:
\begin{equation}
d \mathcal{F}_{\mathbb{H}_{t}}= \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}=0
\label{eq:8}
\end{equation}
We substitute formula \eqref{eq:2} and obtain the equation
\begin{equation}
  \left( \sum_{i}\left[-\frac{2h_{i}}{w_{i}^{2}} +\frac{2}{w_{i}}\partial_{w_{i}}\right]+\frac{\kappa}{2}\sum_{i,j}\partial_{w_{i}} \partial_{w_{j}}\right)\mathcal{F}(\left\{z_{i}\right\})=0
\label{eq:23}
\end{equation}

For the correlation functions of secondary fields $L_{-n}\phi$ we have the equation 
\begin{equation}
\left< (L_{-n}\phi)(z) \varphi_{1}\dots \varphi_{N}\right>=\mathcal{L}_{-n}\left<\phi\varphi_{1}\dots\varphi_{N}\right>,
\end{equation}
 where $n\geq 1$ and
\begin{equation*}
  \mathcal{L}_{-n}=\sum_{i=1}^{N} \left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}} -\frac{1}{(w_{i}-z)^{n-1}}\partial_{w_{i}}\right)
\end{equation*}
(See \cite{difrancesco1997cft}). So we can rewrite the differential equation \eqref{eq:23} as the algebraic equation on the field $\phi$ corresponding to boundary condition changing operator:
\begin{equation}
  \label{eq:24}
   \left<\left([L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi\right)(0)\; \varphi_{\lambda_{1}}\dots \varphi_{\lambda_{{2N}}}\right>=0.
\end{equation}
In the case of minimal models the set of primary fields is finite and all the states are obtained through field-state correspondence \cite{belavin1984ics}, \cite{difrancesco1997cft}. 
Equation \eqref{eq:24}  holds for arbitrary observable $\mathcal{O}$ and arbitrary primary fields $\varphi_{\lambda_{i}}$, so $\psi=[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ is level two null field and $\psi(0)\left|0\right>$ is level two null-state. There exist only two primary fields in minimal unitary models which give rise to Verma modules of Virasoro algebra with level two null-states. They are $\phi_{1,2}$ and $\phi_{2,1}$, so $\phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}$.

>>>>

В статье \cite{schramm2000scaling} было показано, что  $g_{t}(z)$ удовлетворяет стохастическому дифференциальному уравнению
\begin{equation}
\label{eq:19}
  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
\end{equation}
здесь $\xi_{t}$ -- Броуновское движение. Динамика конца  $z_{t}$ критической кривой $\gamma_{t}$ (конец следа эволюции Шрамма-Левнера) описывается уравнением $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.

Стохастический процесс, который удовлетворяет уравнению \eqref{eq:19} называется {\it эволюцией Шрамма-Левнера} на верхней полуплоскости $\mathbb{H}$. Для нас будет удобнее использовать отображение $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, так что уравнение \eqref{eq:19} переписывается в виде
\begin{equation}
  \label{eq:20}
       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}  
\end{equation}
Эволюция Шрамма-Левнера порождает конформно-инвариантную вероятностную меру на кривых $\gamma_{t}$ в $\mathbb{H}$.

\subsection{Мартингалы эволюции Шрамма-Левнера и корреляционные функции в конформной теории поля}
\label{sec:corr-betw-sle}

Теперь рассмотрим наблюдаемые в присутствии следа эволюции Шрамма-Левнера. Математическое ожидание решеточной наблюдаемой $\mathcal{O}$ на верхней полуплоскости можно вычислить как сумму ожиданий этой наблюдаемой в присутствии (конечной части) траектории эволюции Шрамма-Левнера  $\gamma_{t}$ вплоть до некоторого времени $t$, умноженных на вероятность этой траектории:
\begin{equation*}
  \prec \mathcal{O} \succ_{\mathbb{H}}=\mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=\sum_{\gamma_{t}} P\left[C_{\gamma_{t}}\right] \prec \mathcal{O} \succ_{\gamma_{t}}
\end{equation*}
Решеточная наблюдаемая  $\prec \mathcal{O} \succ_{\mathbb{H}}$ не зависит от  $t$, следовательно $\prec\mathcal{O}\succ_{\gamma_{t}}$ -- мартингал.

В непрерывном пределе решеточные наблюдаемые сходятся к корреляционным функциям в конформной теории поля \cite{bauer2003sle,bauer2003conformal,bauer2002sle}. Мы должны учесть изменение граничных условий на конце следа эволюции Шрамма-Левнера и на бесконечности, так что соотношение имеет вид:
\begin{equation}
  \prec \mathcal{O} \succ_{\mathbb{H}_{t}}\to \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}
%% =
%%   \frac{\left<^{g_{t}}
%% \mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
\label{eq:21}
\end{equation}

%% Here $\phi(z_{t})$ is a primary field corresponding to boundary condition changing operator.
%% We've used the conformal map $g_{t}$ to get the expression on the whole plane in equation \eqref{eq:21}.
Мы рассматриваем теорию с границей, так что мы должны использовать модели граничной конформной теории поля и накладывать соответствующие граничные условия \cite{cardy1984conformal,cardy1989boundary,cardy1991bulk}. В случае верхней полуплоскости корреляционные функции в граничной конформной теории поля могут быть переписаны как корреляционные функции для теории на всей плоскости, но с удвоенным числом полей.

@@

Мы предполагаем, что $\mathcal{F}$ содержит некоторый набор примарных полей  $\varphi_{\lambda_{i}}$ с конформными весами $h_{\lambda_{i}}$. Так как мы рассматриваем граничную конформную теорию поля, мы должны добавить объемные поля в сопряженных точках  $\bar z_{i}$. Для дальнейшего использования в моделях Весса-Зумино-Новикова-Виттена мы обозначим конформные веса этих сопряженных полей через $h_{\lambda_{i}^{*}}$. Кроме того, у нас есть операторы смены граничного условия   $\phi$ на конце следа эволюции Шрамма-Левнера и на бесконечности. Воспользуемся конформным отображением   $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$, чтобы переписать выражение \eqref{eq:21} на верхней полуплоскости без разреза:
\begin{equation}
  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
  \label{eq:1}
\end{equation}

Теперь нам нужно рассмотреть, как преобразуется конец следа эволюции Шрамма-Левнера  $\gamma_{t}$ при переходе от времени $t$ к $t+ dt$. Первый множитель в правой части уравнения  (\ref{eq:1}) дает нам
\begin{equation*}
  -\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}.
\end{equation*}
Для преобразования примарных полей  $\varphi_{\lambda_{i}}$ имеет место равенство
\begin{equation}
  \label{eq:2}
  d\varphi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\varphi_{\lambda_{i}}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\varphi_{\lambda_{i}}(w_{i}) 
\end{equation}
Мы обозначим генератор этого преобразования через  $\mathcal{G}_{i}$.

Так как $ \prec\mathcal{O}\succ_{\gamma_{t}}$ --  мартингал, математическое ожидание его приращения при эволюции от  $t$ к $t+dt$ равняется нулю
\begin{equation}
  \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=    \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t+dt}}\right], \quad d\mathbb{E}\left[ \prec\mathcal{O}\succ_{\gamma_{t}}\right]=0
\label{eq:22}
\end{equation}
Используем исчисление Ито и получим выражение для дифференциала $\mathcal{F}$:
\begin{equation}
d \mathcal{F}_{\mathbb{H}_{t}}= \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}=0
\label{eq:8}
\end{equation}
Подставим формулу \eqref{eq:2} и получим уравнение
\begin{equation}
  \left( \sum_{i}\left[-\frac{2h_{i}}{w_{i}^{2}} +\frac{2}{w_{i}}\partial_{w_{i}}\right]+\frac{\kappa}{2}\sum_{i,j}\partial_{w_{i}} \partial_{w_{j}}\right)\mathcal{F}(\left\{z_{i}\right\})=0
\label{eq:23}
\end{equation}

Для корреляционных функций вторичных полей  $L_{-n}\phi$ имеет место уравнение
\begin{equation}
\left< (L_{-n}\phi)(z) \varphi_{1}\dots \varphi_{N}\right>=\mathcal{L}_{-n}\left<\phi\varphi_{1}\dots\varphi_{N}\right>,
\end{equation}
где $n\geq 1$ и
\begin{equation*}
  \mathcal{L}_{-n}=\sum_{i=1}^{N} \left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}} -\frac{1}{(w_{i}-z)^{n-1}}\partial_{w_{i}}\right)
\end{equation*}
(См. \cite{difrancesco1997cft}). То есть мы можем переписать дифференциальное уравнение \eqref{eq:23} как алгебраическое уравнение на поле $\phi$, соответствующее оператору смены граничных условий:
\begin{equation}
  \label{eq:24}
   \left<\left([L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi\right)(0)\; \varphi_{\lambda_{1}}\dots \varphi_{\lambda_{{2N}}}\right>=0.
\end{equation}
В случае минимальных моделей набор примарных полей конечен и все состояния можно получить через соответствие между полями и состояниями
\cite{belavin1984ics}, \cite{difrancesco1997cft}. 
Равенство \eqref{eq:24} верно для произвольной наблюдаемой $\mathcal{O}$ и для произвольных примарных поле $\varphi_{\lambda_{i}}$, так что $\psi=[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ -- нулевое поле уровня два и $\psi(0)\left|0\right>$ -- нулевое состояние уровня два. В минимальных унитарных моделях существует только два примарных поля, порождающих модули Верма алгебры Вирасоро с нулевыми состояниями на уровне два. Это поля $\phi_{1,2}$ и $\phi_{2,1}$, так что $\phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}$.
